Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-10-04 manuscript.Rmd
Rewrote experiment 3 results

## Experiment 3
The results from the third experiment are shown in figure \@ref(fig:matchingdata). Each curve is showing the contrast level in each eye for the different interocular ratios.

Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line). This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%. These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard. For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%. For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%. When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination. Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.

>>>>

## Experiment 3
The results from the third experiment are shown in figure \@ref(fig:matchingdata). Each curve is showing the contrast level in each eye for the different interocular ratios at the 24 \% (in red) and 48 \% (in blue) conditions.

Looking at the results for the 48 \% contrast condition, we can observe that, when the match was presented binocularly (both eyes saw the same stimulus), the match appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line). This is also observable for the 24 \% contrast condition, where the match appeared to have the same flickering intensity as the standard when the contrast was selected to be around 25 \%. These two results show that the paradigm was working correctly and that the participants could see the flicker properly.

When the match was presented monocularly (only one eye was presented with a flickering stimulus), we observe that, for the match to appear to flicker similarly to the standard, the contrast in that eye was set to be around double the contrast of the standard. When the flicker was presented only to the left eye, for the 48 \% contrast, the contrast of the match was around 90 \%, and, for the 24 \% contrast, the contrast of the match was around 57 \%. When the flicker was presented only to the right eye, for the 48 \% contrast, the contrast in the right eye was around 96 \%, and, for the 24 \% contrast, the contrast was around 50 \%. When looking at the intermediate condition, we can see that the points, for both contrast conditions, seem to fall along the main diagonal representing the linear summation prediction, with the results for the 24 \% condition showing a very strong summation that seem to exceed this prediction. Overall, these results seem to suggest that the way we perceive temporal luminance modulations follows near linear combination rules, which is in line with the processes observed in the visual cortex in experiment 1 (fig. \@ref(fig:EEGdata)).
```{r include=FALSE, results='hide'}

### 2022-10-04 manuscript.tex
Rewrote experiment 3 results

A similar process was adopted for the analysis of the pupillometry data. The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software (Kassner et al., 2014). The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted. Fourier transform was calculated for each waveform, and the spectrum stored in a matrix. All repetitions of each condition were then averaged for each eye. They were then averaged across the two eyes, to obtain individual results. Finally, these were averaged across all participants to obtain the final results.

@@

The results from the third experiment are shown in figure \ref{fig:matchingdata}. Each curve is showing the contrast level in each eye for the different interocular ratios.

Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line). This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%. These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard. For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%. For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%. When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination. Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.

>>>>

A similar process was adopted for the analysis of the pupillometry data. The data were converted from the mp4 format to a csv text file using the Pupil Player software (Kassner et al., 2014). The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted. Fourier transform was calculated for each waveform, and the spectrum stored in a matrix. All repetitions of each condition were then averaged for each eye. They were then averaged across the two eyes, to obtain individual results. Finally, these were averaged across all participants to obtain the final results.

@@

The results from the third experiment are shown in figure \ref{fig:matchingdata}. Each curve is showing the contrast level in each eye for the different interocular ratios at the 24 \% (in red) and 48 \% (in blue) conditions.

Looking at the results for the 48 \% contrast condition, we can observe that, when the match was presented binocularly (both eyes saw the same stimulus), the match appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line). This is also observable for the 24 \% contrast condition, where the match appeared to have the same flickering intensity as the standard when the contrast was selected to be around 25 \%. These two results show that the paradigm was working correctly and that the participants could see the flicker properly.

When the match was presented monocularly (only one eye was presented with a flickering stimulus), we observe that, for the match to appear to flicker similarly to the standard, the contrast in that eye was set to be around double the contrast of the standard. When the flicker was presented only to the left eye, for the 48 \% contrast, the contrast of the match was around 90 \%, and, for the 24 \% contrast, the contrast of the match was around 57 \%. When the flicker was presented only to the right eye, for the 48 \% contrast, the contrast in the right eye was around 96 \%, and, for the 24 \% contrast, the contrast was around 50 \%. When looking at the intermediate condition, we can see that the points, for both contrast conditions, seem to fall along the main diagonal representing the linear summation prediction, with the results for the 24 \% condition showing a very strong summation that seem to exceed this prediction. Overall, these results seem to suggest that the way we perceive temporal luminance modulations follows near linear combination rules, which is in line with the processes observed in the visual cortex in experiment 1 (fig.~\ref{fig:EEGdata}).
